\begin{center}
% {\fontsize{18pt}{20pt}\selectfont \textbf{\underline{ACKNOWLEDGEMENT}}}
    {\fontsize{18pt}{20pt}\bookmanheading{\underline{ACKNOWLEDGEMENT}}}

\end{center}
\addcontentsline{toc}{section}{ACKNOWLEDGEMENT}

I would like to express my sincere gratitude to all those who have contributed to the successful completion of this doctoral research.

First and foremost, I extend my deepest appreciation to my thesis supervisor(s) for their invaluable guidance, continuous encouragement, and insightful feedback throughout this research journey. Their expertise in power systems and control theory has been instrumental in shaping this work, and their patience and support during challenging phases of the research have been truly invaluable.

I am grateful to my co-authors---Dr. Mamoon Aldobali, Dr. Subhojit Bose, Dr. Praveen Dwivedi, Mr. Yousef Alward, and Dr. Shailendra Negi---for their collaborative contributions to the publications arising from this research. Special thanks to Dr. Bose and Dr. Dwivedi for their technical insights on deep reinforcement learning applications in renewable energy systems.

I acknowledge the National Institute of Technology, Uttarakhand, for providing the research facilities, computational resources, and academic environment necessary for conducting this work. I am particularly thankful to the Department of Electrical Engineering for providing access to the OPAL-RT real-time simulator platform, which was crucial for the Hardware-in-Loop validation experiments presented in this thesis.

My sincere thanks to the faculty members and research scholars of NIT Uttarakhand who provided valuable suggestions during research seminars and discussions. Their constructive feedback helped refine the research methodology and strengthen the experimental validation framework.

I gratefully acknowledge the use of computational resources provided by Google Colab Pro for training the deep reinforcement learning controllers, and the NREL (National Renewable Energy Laboratory) for providing publicly available wind and solar irradiance datasets used in this research.

I would like to thank the reviewers and editors of \textit{Scientific Reports} and other journals where parts of this work have been published or are under review. Their critical comments and suggestions significantly improved the quality and clarity of this research.

I am deeply indebted to my family for their unwavering love, support, and encouragement throughout my doctoral studies. Their understanding and patience during the long hours of research and writing made this achievement possible.

Finally, I thank all my friends and colleagues who provided moral support and created a positive environment conducive to research and learning.

\vspace{1cm}

\begin{flushright}
\textbf{Ruchir Pandey}\\
National Institute of Technology, Uttarakhand\\
2025
\end{flushright}